\Large\bf FlexibleSUSY --- A spectrum generator generator for supersymmetric models

### 2014-11-18 doc/flexiblesusy-paper.tex
describe new feature ExtraSLHAOutputBlocks

DefaultPoleMassPrecision = MediumPrecision;
HighPoleMassPrecision    = {hh, Ah, Hpm};
MediumPoleMassPrecision  = {};
LowPoleMassPrecision     = {};
\end{lstlisting}
%
The first line \code{FSModelName = "@CLASSNAME@";} will be replaced
with \code{FSModelName = "<model>";} in the generated
\code{FlexibleSUSY.m} file, where \code{<model>} is specified by the
\code{--name=<model>} option for the \code{./createmodel} script.  So
the variable \code{FSModelName} then contains the name of the \fs
model.

@@

>>>>

DefaultPoleMassPrecision = MediumPrecision;
HighPoleMassPrecision    = {hh, Ah, Hpm};
MediumPoleMassPrecision  = {};
LowPoleMassPrecision     = {};

(* optional *)
ExtraSLHAOutputBlocks = {
   {ALPHA, {{ArcCos[Pole[ZH[1,2]]]}}},
   {HMIX , {{1, \[Mu]},
            {2, vu / vd},
            {3, Sqrt[vu^2 + vd^2]},
            {4, M[Ah[2]]^2},
            {101, B[\[Mu]]},
            {102, vd},
            {103, vu} } },
   {Au,    {{1, 1, T[Yu][1,1] / Yu[1,1]},
            {2, 2, T[Yu][2,2] / Yu[2,2]},
            {3, 3, T[Yu][3,3] / Yu[3,3]} } },
   {Ad,    {{1, 1, T[Yd][1,1] / Yd[1,1]},
            {2, 2, T[Yd][2,2] / Yd[2,2]},
            {3, 3, T[Yd][3,3] / Yd[3,3]} } },
   {Ae,    {{1, 1, T[Ye][1,1] / Ye[1,1]},
            {2, 2, T[Ye][2,2] / Ye[2,2]},
            {3, 3, T[Ye][3,3] / Ye[3,3]} } },
   {MSOFT, {{1, MassB},
            {2, MassWB},
            {3, MassG},
            {21, mHd2},
            {22, mHu2},
            {31, Sqrt[ml2[1,1]]},
            {32, Sqrt[ml2[2,2]]},
            {33, Sqrt[ml2[3,3]]},
            {34, Sqrt[me2[1,1]]},
            {35, Sqrt[me2[2,2]]},
            {36, Sqrt[me2[3,3]]},
            {41, Sqrt[mq2[1,1]]},
            {42, Sqrt[mq2[2,2]]},
            {43, Sqrt[mq2[3,3]]},
            {44, Sqrt[mu2[1,1]]},
            {45, Sqrt[mu2[2,2]]},
            {46, Sqrt[mu2[3,3]]},
            {47, Sqrt[md2[1,1]]},
            {48, Sqrt[md2[2,2]]},
            {49, Sqrt[md2[3,3]]} } }
};
\end{lstlisting}
%
The first line \code{FSModelName = "@CLASSNAME@";} will be replaced
with \code{FSModelName = "<model>";} in the generated
\code{FlexibleSUSY.m} file, where \code{<model>} is specified by the
\code{--name=<model>} option for the \code{./createmodel} script.  So
the variable \code{FSModelName} then contains the name of the \fs
model.

@@

Finally, with the variable \code{ExtraSLHAOutputBlocks} the user can
define extra SLHA output blocks.  The values of the block entries will
be calculated at the output scale, which is specified in entry $12$ in
the SLHA input block \code{MODSEL}.  In the example model file above
the following six extra SLHA compliant output blocks are defined:
\code{ALPHA}, \code{HMIX}, \code{Au}, \code{Ad}, \code{Ae} and
\code{MSOFT}.  The \code{ALPHA} output block contains the CP-even
Higgs pole mass mixing angle as the only entry.  The \code{HMIX}
output block contains the $\mu$-parameter, the ratio $\tan\beta =
v_u/v_d$, the combination $v=\sqrt{v_u^2 + v_d^2}$, the squared mass
of the CP-odd Higgs $m_A^2$, the soft-breaking parameter $B\mu$ and
the values of $v_u$ and $v_d$, all defined in the \DRbar\ scheme.  In
an analogue way four more output blocks for the soft-breaking \DRbar\
parameters are defined.  For a CMSSM example parameter point with $m_0
= 125\unit{GeV}$, $M_{1/2} = 500\unit{GeV}$, $\tan\beta = 10$,
$\sign\mu = +1$ and $A_0 = 0$ the \fs-generated CMSSM spectrum
generator writes the so defined blocks to the output in the form
%
\begin{lstlisting}
Block ALPHA Q= 8.76740936E+02
           1.06784138E-01   # ArcCos(Pole(ZH(0,1)))
Block HMIX Q= 8.76740936E+02
     1     6.31218384E+02   # Mu
     2     9.67312621E+00   # vu/vd
     3     2.44053433E+02   # Sqrt(Sqr(vd) + Sqr(vu))
     4     5.36777230E+05   # Sqr(MAh(1))
   101     5.49048159E+04   # BMu
   102     2.50962986E+01   # vd
   103     2.42759663E+02   # vu
Block Au Q= 8.76740936E+02
  1  1    -1.14477419E+03   # TYu(0,0)/Yu(0,0)
  2  2    -1.14476911E+03   # TYu(1,1)/Yu(1,1)
  3  3    -8.83902977E+02   # TYu(2,2)/Yu(2,2)
Block Ad Q= 8.76740936E+02
  1  1    -1.40026447E+03   # TYd(0,0)/Yd(0,0)
  2  2    -1.40025976E+03   # TYd(1,1)/Yd(1,1)
  3  3    -1.30885006E+03   # TYd(2,2)/Yd(2,2)
Block Ae Q= 8.76740936E+02
  1  1    -3.00005426E+02   # TYe(0,0)/Ye(0,0)
  2  2    -3.00000006E+02   # TYe(1,1)/Ye(1,1)
  3  3    -2.98364373E+02   # TYe(2,2)/Ye(2,2)
Block MSOFT Q= 8.76740936E+02
     1     2.09018579E+02   # MassB
     2     3.88257873E+02   # MassWB
     3     1.11544211E+03   # MassG
    21     1.09683411E+05   # mHd2
    22    -3.85898988E+05   # mHu2
    31     3.54416224E+02   # Sqrt(ml2(0,0))
    32     3.54412891E+02   # Sqrt(ml2(1,1))
    33     3.53407333E+02   # Sqrt(ml2(2,2))
    34     2.22035720E+02   # Sqrt(me2(0,0))
    35     2.22024873E+02   # Sqrt(me2(1,1))
    36     2.18731935E+02   # Sqrt(me2(2,2))
    41     1.02053367E+03   # Sqrt(mq2(0,0))
    42     1.02053107E+03   # Sqrt(mq2(1,1))
    43     9.40760849E+02   # Sqrt(mq2(2,2))
    44     9.82565930E+02   # Sqrt(mu2(0,0))
    45     9.82563167E+02   # Sqrt(mu2(1,1))
    46     8.09126982E+02   # Sqrt(mu2(2,2))
    47     9.77979392E+02   # Sqrt(md2(0,0))
    48     9.77976666E+02   # Sqrt(md2(1,1))
    49     9.73121951E+02   # Sqrt(md2(2,2))
\end{lstlisting}
